Limited evidence for widespread heterogeneity in psychology

### 2018-11-14 writing/appendixA-heterogeneity.rmd
Re-added appendices since one of them includes a table

Appendix A - Sensitivity analysis of effect size for simulations

In our main results we simulated data to estimate type I error and power using an average effect size of zero. As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity. However, as a sensitivity analysis we in this Appendix again estimate type I error and power, but generated with an average 'medium' effect size as defined by Cohen (1988).

Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs. medium are shown for each effect in Table A1. In both cases type I error is approximately nominal, as compared to the expected 5% error rate. With a an effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity respectively. The corresponding power with an average effect size was `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%. To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.

@@

_Type I error and power to detect four heterogeniety levels under two true effect sizes_

>>>>

Appendix A - Sensitivity analysis assuming a medium true effect size rather than zero true effect size

In our main results we simulated data to estimate type I error and power using an average true effect size equal to zero. As explained in the methods section this is unlikely to matter as our interest lies in heterogeneity. However, as a sensitivity analysis, in this appendix we also estimated type I error and power, but generated with an average 'medium' true effect size as defined by Cohen (1988).

Estimated type I error and power for zero/small/medium/large heterogeneity when simulated with a true effect size of zero vs. medium are shown for each effect in Table A1. In both cases type I error is approximately nominal, as compared to the expected 5% error rate. With a true effect size of zero, average power was `r 100*round(mean(zero$Small), digits = 2)`%/`r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`% for small/medium/large heterogeneity, respectively. The corresponding power with a true medium effect size was also `r 100*round(mean(zero$Small), digits = 2)`%/ `r 100*round(mean(zero$Medium), digits = 2)`%/`r 100*round(mean(zero$Large), digits = 2)`%, respectively. To conclude, changing true effect size in our simulations from zero to medium had little to no impact on estimated type I error and power.

@@

_Type I error and power to detect four heterogeneity levels under two true effect sizes_

### 2018-11-14 writing/appendixB-heterogeneity.rmd
Re-added appendices since one of them includes a table

This appendix describes the formulas used to convert effect sizes into a common effect size measure (correlations). All formulas presented can be found in Borenstein (2009) and page numbers are cited as formulas are presented. For (standardized) mean differences, We assumed equal population standard deviations $\sigma_1 = \sigma_2$, and calculated (p. 226) the pooled standard deviation $S_p$ as follows:

@@

Where $n_1$/$n_2$ are group sample sizes and $S_1^2$/$S_2^2$ are the sample variances. In one case (RR8) we had to convert reported standard errors into pooled standard deviations. Standard errors are the square root of the variance of the mean:

@@

Where $d$ is the standardized mean difference and $\bar{x}_1$/$\bar{x}_2$ the sample means of the two groups. We finally converted effect sizes to correlaions $r$ (p. 234):

@@

For effects that were reported as odds ratios or risk differences, we computed log odds ratios, converted these to standardized mean differences, and proceeded as above to convert these to correlations. We first added one half to any empty cell to avoid dividing by zero. We then computed the log odds ratios as follows (p. 266):

$$OR_{log} = ln \frac{a \times d}{b \times c}$$
Where $a$, $b$, $c$, and $d$ are the four cell sizes. The log odds ratios were converted to $d$s as follows (p. 232):

>>>>

This appendix describes the formulas used to convert effect sizes into a common effect size measure (correlations). All formulas presented can be found in Borenstein (2009). For (standardized) mean differences, we assumed equal population standard deviations $\sigma_1 = \sigma_2$, and calculated (p. 226) the pooled standard deviation $S_p$ as follows:

@@

where $n_1$/$n_2$ are group sample sizes and $S_1^2$/$S_2^2$ are the sample variances. In one case (RR8) we had to convert reported standard errors into pooled standard deviations. Standard errors are the square root of the variance of the mean:

@@

where $d$ is the standardized mean difference and $\bar{x}_1$/$\bar{x}_2$ the sample means of the two groups. We finally converted effect sizes to correlations (p. 234):

@@

For effects that were measured as odds ratios (transformed by ML1 into standardized mean difference) or risk differences, we computed log odds ratios, converted these to standardized mean differences, and proceeded as above to convert these to correlations. We first added one half to any empty cell to avoid dividing by zero and then computed the log odds ratios as follows (p. 266):

$$OR_{log} = ln \frac{a \times d}{b \times c}$$
where $a$, $b$, $c$, and $d$ are the four cell sizes. The log odds ratios were converted to $d$s as follows (p. 232):
